The \Prob

### 2013-03-07 bikes/bikes.tex
bikes: contiguous and conclusion

\newcommand\PA{\ensuremath{\mathsf{i}}}
\newcommand\PB{\ensuremath{\mathsf{ii}}}
\newcommand\PC{\ensuremath{\mathsf{iii}}}
\newcommand\PD{\ensuremath{\mathsf{iv}}}
\newcommand\PE{\ensuremath{\mathsf{v}}}
Formally we say that the {\em bicycle allocation} for this case is that person \PA~(the blue one, if you're reading this electronically or printed in color) rides bike $0$ for distances between $0$ and $1$, and person \PB~(the red one, if same) rides it for distances between $1$ and $2$. For short, we write:
\begin{eqnarray*}
	p_\PA &=& b_0@0 \\
	p_\PB &=& b_0@1
\end{eqnarray*}

@@

\newcommand\BA{\cellcolor{WildStrawberry}~\textcolor{White}{$b_0$}}
\newcommand\BB{\cellcolor{NavyBlue}      ~\textcolor{White}{$b_1$}}
\newcommand\BC{\cellcolor{OliveGreen}   ~\textcolor{White}{$b_2$}}
\newcommand\BD{\cellcolor{Dandelion}    ~\textcolor{White}{$b_3$}}
\begin{figure*}[t]
	\begin{subfigure}[b]{0.28\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|}
		& \multicolumn{2}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \\
		\cline{2-3}
		\multicolumn{1}{r|}{\PB} & & \BA \\
		\cline{2-3}
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\end{tabular}
		\caption{$2$ people, $1$ bike.}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{3}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} & \multicolumn{1}{c|}{2} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \BB & \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PB} & & \BA & \BB \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PC} & \BB & & \BA \\
		\cline{2-4}
		\multicolumn{4}{c}{}\\
		\multicolumn{4}{c}{}\\
		\end{tabular}
		\caption{$3$ people, $2$ bikes.}
	\end{subfigure}
	\begin{subfigure}[b]{0.38\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{5}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} & \multicolumn{1}{c|}{2} & \multicolumn{1}{c|}{3} & \multicolumn{1}{c|}{4} \\
		\hline
		\multicolumn{1}{r|}{\PA} &\BA&\BB&\BC&   & \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PB} &   &\BA&\BB&\BC& \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PC} &   &   &\BA&\BB&\BC\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PD} &\BC&   &   &\BA&\BB\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PE} &\BB&\BC&   &   &\BA\\
		\cline{2-6}
		\end{tabular}
		\caption{$5$ people, $3$ bikes.}
	\end{subfigure}
	\caption{Bicycle allocation policies for selected instances of the \prob. White cells represent walking; cells of different colours represent different bikes.
		Can you spot the French flag?}
	\label{fig:grids}
\end{figure*}

@@

\begin{figure}[b]
		\begin{center}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{5}{c}{distance} \\
		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} & \multicolumn{1}{c|}{2} & \multicolumn{1}{c|}{3} & \multicolumn{1}{c|}{4} \\
		\hline
		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&   & \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB& \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PD} &\BB&   &   &\BA&\BA\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BB\\
		\cline{2-6}
		\end{tabular}
		\end{center}
		\caption{Each person mounts/dismounts 2 or 4 times.}
		\label{fig:continuous}
\end{figure}

@@

\begin{theorem}[Contiguous Allocation]
woo
% TODO
\end{theorem}
\begin{proof}
woo
%TODO
\end{proof}
%\begin{figure}[b]
%		\begin{center}
%			\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
%		& \multicolumn{6}{c}{distance} \\
%		person & \multicolumn{1}{|c|}{0} & \multicolumn{1}{c|}{1} & \multicolumn{1}{c|}{2} & \multicolumn{1}{c|}{3} & \multicolumn{1}{c|}{4} & \multicolumn{1}{c|}{5} \\
%		\hline
%		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&\BA&   &   \\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&\BB&   \\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC&\BC\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PD} &\BB&   &   &\BD&\BD&\BD\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BA&\BA\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{fff} &\BD&\BD&\BD&   &   &\BB\\
%		\cline{2-7}
%		\end{tabular}
%		\end{center}
%		\caption{Scratch work}
%\end{figure}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.75\textwidth]{graph.pdf}
	\caption{Speedup achieved in the \prob. As always, lower is better.}
	\label{fig:graph}
\end{figure*}
%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

>>>>

\newcommand\PA{\ensuremath{\mathtt{0}}}
\newcommand\PB{\ensuremath{\mathtt{1}}}
\newcommand\PC{\ensuremath{\mathtt{2}}}
\newcommand\PD{\ensuremath{\mathtt{3}}}
\newcommand\PE{\ensuremath{\mathtt{4}}}
\newcommand\distance[1]{\ensuremath{\mathsf{#1}}}
Formally we say that the {\em bicycle allocation} for this case is that person \PA~(the blue one, if you're reading this electronically or printed in color) rides bike $0$ for distances between $0$ and $1$, and person \PB~(the red one, if same) rides it for distances between $1$ and $2$. For short, we write:
\begin{eqnarray*}
	p_\PA &=& b_0@0 \\
	p_\PB &=& b_0@1
\end{eqnarray*}

@@

\newcommand\BA{\cellcolor{WildStrawberry}~\textcolor{White}{$b_0$}}
\newcommand\BB{\cellcolor{NavyBlue}      ~\textcolor{White}{$b_1$}}
\newcommand\BC{\cellcolor{OliveGreen}   ~\textcolor{White}{$b_2$}}
\newcommand\BD{\cellcolor{Dandelion}    ~\textcolor{White}{$b_3$}}
\newcommand\BE{\cellcolor{ProcessBlue}       ~\textcolor{White}{$b_3$}}
\begin{figure*}[t]
	\begin{subfigure}[b]{0.28\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|}
		& \multicolumn{2}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \\
		\cline{2-3}
		\multicolumn{1}{r|}{\PB} & & \BA \\
		\cline{2-3}
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\multicolumn{3}{c}{}\\
		\end{tabular}
		\caption{$2$ people, $1$ bike.}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{3}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} \\
		\hline
		\multicolumn{1}{r|}{\PA} & \BA & \BB & \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PB} & & \BA & \BB \\
		\cline{2-4}
		\multicolumn{1}{r|}{\PC} & \BB & & \BA \\
		\cline{2-4}
		\multicolumn{4}{c}{}\\
		\multicolumn{4}{c}{}\\
		\end{tabular}
		\caption{$3$ people, $2$ bikes.}
	\end{subfigure}
	\begin{subfigure}[b]{0.38\textwidth}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{5}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} \\
		\hline
		\multicolumn{1}{r|}{\PA} &\BA&\BB&\BC&   & \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PB} &   &\BA&\BB&\BC& \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PC} &   &   &\BA&\BB&\BC\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PD} &\BC&   &   &\BA&\BB\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PE} &\BB&\BC&   &   &\BA\\
		\cline{2-6}
		\end{tabular}
		\caption{$5$ people, $3$ bikes.}
	\end{subfigure}
	\caption{Bicycle allocation policies for selected instances of the \prob. White cells represent walking; cells of different colours represent different bikes.
		Can you spot the French flag?}
	\label{fig:grids}
\end{figure*}

@@

\begin{figure}[b]
		\begin{center}
		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
		& \multicolumn{5}{c}{distance} \\
		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} \\
		\hline
		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&   & \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB& \\
		\cline{2-6}
		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PD} &\BB&   &   &\BA&\BA\\
		\cline{2-6}
		\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BB\\
		\cline{2-6}
		\end{tabular}
		\end{center}
		\caption{Each person mounts/dismounts 2 or 4 times.}
		\label{fig:continuous}
\end{figure}

@@

\begin{theorem}[Contiguous Allocation]
For all $n$ and $k$, an optimal bicycle allocation exists in which no rider mounts and dismounts more than four times, and is given as follows:
\newcommand\open{\{}
\newcommand\close{\}}
\begin{center}
\begin{tabular}{rclll}
	$p_i$ & $=$ & $b_{(i~\mathsf{mod}~k)}@ \open i \rightsquigarrow i+k \close$ && $i \le n-k$ \\
	\\
	\multirow{2}{*}{$p_i$} & \multirow{2}{*}{$=$} & $b_{(i~\mathsf{mod}~k)}@ \open i\rightsquigarrow n \close,$ && \multirow{2}{*}{$i > n-k$} \\
	& & $b_{(i+k-n)}\hspace{0.5em}@ \open 0 \rightsquigarrow i+k-n \close$ \\
	\\
\end{tabular}
\end{center}
where $b_x@\open y\rightsquigarrow z\close$ expands to $b_x@(y)$, $b_x@(y+1)$, \dots $b_x@(z-1)$.

\end{theorem}
\begin{proof}
By induction on $k$.
\end{proof}

%\begin{figure}[b]
%		\begin{center}
%			\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
%		& \multicolumn{6}{c}{distance} \\
%		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} \\
%		\hline
%		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&\BA&   &   \\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&\BB&   \\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC&\BC\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PD} &\BB&   &   &\BD&\BD&\BD\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PE} &\BC&\BC&   &   &\BA&\BA\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{fff} &\BD&\BD&\BD&   &   &\BB\\
%		\cline{2-7}
%		\end{tabular}
%		% 6/4
%			\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
%		& \multicolumn{6}{c}{distance} \\
%		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} \\
%		\hline
%		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&\BA&\BA&   \\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&\BB&\BB\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PC} &\BB&   &\BC&\BC&\BC&\BC\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PD} &\BC&\BC&   &\BD&\BD&\BD\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{\PE} &\BD&\BD&\BD&   &\BE&\BE\\
%		\cline{2-7}
%		\multicolumn{1}{r|}{fff} &\BE&\BE&\BE&\BE&   &\BA\\
%		\cline{2-7}
%		\end{tabular}
%		% 7/3
%		\begin{tabular}{rp{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|p{1.5em}|}
%		& \multicolumn{7}{c}{distance} \\
%		person & \multicolumn{1}{|c|}{\distance{0}} & \multicolumn{1}{c|}{\distance{1}} & \multicolumn{1}{c|}{\distance{2}} & \multicolumn{1}{c|}{\distance{3}} & \multicolumn{1}{c|}{\distance{4}} & \multicolumn{1}{c|}{\distance{5}} & \multicolumn{1}{c|}{\distance{6}}\\
%		\hline
%		\multicolumn{1}{r|}{\PA} &\BA&\BA&\BA&   &   &   &   \\
%		\cline{2-8}
%		\multicolumn{1}{r|}{\PB} &   &\BB&\BB&\BB&   &   &   \\
%		\cline{2-8}
%		\multicolumn{1}{r|}{\PC} &   &   &\BC&\BC&\BC&   &   \\
%		\cline{2-8}
%		\multicolumn{1}{r|}{\PD} &   &   &   &\BA&\BA&\BA&   \\
%		\cline{2-8}
%		\multicolumn{1}{r|}{\PE} &   &   &   &   &\BB&\BB&\BB\\
%		\cline{2-8}
%		\multicolumn{1}{r|}{fff} &\BB&   &   &   &   &\BC&\BC\\
%		\cline{2-8}
%		\multicolumn{1}{r|}{ggg} &\BC&\BC&   &   &   &   &\BA\\
%		\cline{2-8}
%		\end{tabular}
%		\end{center}
%		\caption{Scratch work}
%\end{figure}

@@

\section{Conclusion}

\initial{Y}ou and your friends have arrived at $d$ at the unprecedentedly fast speed of $nbw/(kw+bn-bk)$, and are warming up indoors and enjoying dinner. ``Wow,'' you say, ``I sure am glad everyone thought to make $n$ copies of their bike-lock keys!''

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.85\textwidth]{graph.pdf}
	\caption{Speedup achieved in the \prob. As always, lower is better.}
	\label{fig:graph}
\end{figure*}
%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
